### 2013-01-08 ISMB/results_ISMB.tex
Some typos + figs

\begin{figure}[ht!]
	\centering
	\includegraphics[scale=0.45]{Figures/time_rnastrand_clustered_rnainverse_100samples_fix}
	\caption{Average time in seconds to generate one sequence. We explicitly show 
	the time spent by \texttt{Incarnation} (full line) and \texttt{RNAinverse} (dashed) for various \texttt{G+C} contents. The first plot is in function
	of the length of the structures. The second is in function of the stack
	density (i.e. $2\cdot\#stacks/length$) and the latter in function of 
	the proportion of free nucleotides (i.e. not base paired) inside loops.}
	\label{fig:time}	
\end{figure}

\subsection{Dataset}
To evaluate the quality of our method, we selected a subset of $50$ secondary
structures from the \textit{RNA STRNAD} database~\cite{andronescu2008rna}.
Those are known secondary structure from a variety of organisms with 
 lengths between $20$ and $100$ nucleotides.

@@

 \begin{figure}[ht!]
 	\centering
	\includegraphics[scale=0.45]{Figures/bins_distribution.png}
	\caption{Number of secondary structures per bins.}
	\label{fig:bins}
 \end{figure}

@@

\begin{figure}[ht!]	
	\centering
	\includegraphics[scale=0.45]{Figures/mfe_struct_solve_nornainverse.png}
	\caption{Quality of \texttt{Incarnation} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure}

\begin{figure}[ht!]	
	\centering
	\includegraphics[scale=0.45]{Figures/mfe_struct_solved}
	\caption{Quality of \texttt{Incarnation+RNAinverse} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[width=1\textwidth,height=0.16\textheight]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[scale=0.45]{Figures/nb_sols_entropy.png}
	\caption{Number of solutions generated and their average entropy. 
	The last row presents only the entropy of the nucleotides inside base 
	pairs.}
	\label{fig:nb_sols_entropy}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[scale=0.45]{Figures/freq.png}
	\caption{Average frequency of the MFE.}
	\label{fig:freq}
\end{figure}

>>>>

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/time_rnastrand_clustered_rnainverse_100samples_fix}
	\caption{Average time in seconds to generate one sequence. We explicitly show 
	the time spent by \texttt{Incarnation} (full line) and \texttt{RNAinverse} (dashed) for various \texttt{G+C} contents. The first plot is in function
	of the length of the structures. The second is in function of the stack
	density (i.e. $2\cdot\#stacks/length$) and the latter in function of 
	the proportion of free nucleotides (i.e. not base paired) inside loops.}
	\label{fig:time}	
\end{figure}

\subsection{Dataset}
To evaluate the quality of our method, we selected a subset of $50$ secondary
structures from the \textit{RNA STRAND} database~\cite{andronescu2008rna}.
Those are known secondary structure from a variety of organisms with 
 lengths between $20$ and $100$ nucleotides.

@@

 \begin{figure}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{Figures/bins_distribution.png}
	\caption{Number of secondary structures per bins.}
	\label{fig:bins}
 \end{figure}

@@

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{Figures/mfe_struct_solve_nornainverse.png}
	\caption{Quality of \texttt{Incarnation} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved_noinverse}	
\end{figure}

\begin{figure}[ht!]	
	\centering
	\includegraphics[width=\textwidth]{Figures/mfe_struct_solved}
	\caption{Quality of \texttt{Incarnation+RNAinverse} results. The first row shows the percentage
	of sampled sequences folding into the target. The second shows the 	
	proportion	of structures for which at least one correct sequence was 
	sampled.}
	\label{fig:mfe_struct_solved}	
\end{figure}

@@

\begin{figure}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	%\includegraphics[width=1\textwidth,height=0.16\textheight]{Figures/rnastrand_clustered_rnainverse_100samples_struct_sens.png}
	\caption{Structural sensitivity (i.e. $\#$ well predicted base pairs / $\#$ base pairs in target) of the sampled sequences MFE. }
	\label{fig:ss_sens}	
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/nb_sols_entropy.png}
	\caption{Number of solutions generated and their average entropy. 
	The last row presents only the entropy of the nucleotides inside base 
	pairs.}
	\label{fig:nb_sols_entropy}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\textwidth]{Figures/freq.png}
	\caption{Average frequency of the MFE.}
	\label{fig:freq}
\end{figure}
